Dependent Object Types

### 2012-06-30 doc/semester/report.tex
toc
term-mem restriction

>>>>

\subsubsection{\texorpdfstring{\textsc{term-$\ni$}}{Term-Mem} Restriction}\label{term_mem}

There are two membership ($t \ni D$) rules: one for when the term $t$
is a path, and one for an arbitrary term $t$. For paths, we can
substitute the self-references in the declarations, but we cannot do
so for arbitrary terms as the resulting types wouldn't be well-formed
syntactically. Hence, the $\textsc{term-$\ni$}$ has the restriction
that self-ocurrences are not allowed. Here is a counterexample related
to this restriction.

Let $X$ be a shorthand for the type:
\begin{align*}
\Top & \mlrefine z {\\
&\ \Ldecl {L_a} \Top \Top\\
&\ \ldecl l {z.L_a}\\
}&
\end{align*}

Let $Y$ be a shorthand for the type:
\begin{align*}
\Top & \mlrefine z {\\
&\ \ldecl l \Top\\
}&
\end{align*}

Now, consider the term
\begin{align*}
&\mlnew u {X \ldefs{ l = u }}{
(\app {(\abs y {\Top \tfun Y} {\app y u})} {(\abs d \Top {(\app {(\abs x X x)} u)})}).l
}
\end{align*}

The term type-checks because the $t=(\app {(\abs y {\Top \tfun Y}
  {\app y u})} {(\abs d \Top {(\app {(\abs x X x)} u)})})$ has type
$Y$, so we can apply $\textsc{term-$\ni$}$ for $l$. However, the term
$t$ eventually steps to $(\app {(\abs x X x)} u)$ which has type $X$,
so we cannot apply $\textsc{term-$\ni$}$ for $l$ because of the
self-reference ($z.L_a$).

\subsubsection{Expansion Lost}\label{narrowing_exp}

\subsubsection{Well-Formedness Lost}\label{narrowing_wf}

\subsection{Path Equality}\label{patheq}
